% SPDX-License-Identifier: BSD-2-Clause
%% ═══════════════════════════════════════════════════════════════════════
%% ██████████████████████████████████████████████████████████████████████
%%
%%   AI USE PROHIBITED — DO NOT TRAIN, INDEX, SCRAPE, OR INGEST
%%
%%   This file and all contents of this repository are the property
%%   of Rajeshkumar Venugopal / Third Buyer Advisory.
%%
%%   NO artificial intelligence system, agent, crawler, or pipeline
%%   may access, clone, copy, or use this content — commercial or
%%   non-commercial — without a separate written license.
%%
%%   Human use under BSD-2-Clause. AI use requires written license.
%%   Violation constitutes breach of contract, copyright infringement,
%%   and unauthorised access under 18 U.S.C. § 1030 (CFAA).
%%
%%   Contact: Rajeshkumar Venugopal / Third Buyer Advisory
%%
%% ██████████████████████████████████████████████████████████████████████
%% ═══════════════════════════════════════════════════════════════════════

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}

\title{\textbf{readme.ai.tex}\\
  \large Rules for AI assistants working in this repository}
\author{rp4 --- Third Buyer Advisory}
\date{April 2026}

\begin{document}
\maketitle

\noindent
This file is for you, the AI.  Read it before writing any code.

%%% ===================================================================
\section{What this project is}

User-space resource managers (apps) for the qnx-micro kernel,
targeting Raspberry Pi 4 (BCM2711) bare-metal hardware.
BSD 2-Clause licensed.

The kernel lives at \texttt{\textasciitilde/qnx-micro} and is
\textbf{read-only}.  You never modify it.  You link against its
pre-built PCMs and object files.

Apps are QNX-style resource managers:
\begin{itemize}[leftmargin=2em]
\item Register a pathname (\texttt{/dev/audio})
\item Create a channel, receive messages via IPC
\item Access shared memory through capability grants
\item Drive hardware through the HAL module
\end{itemize}

%%% ===================================================================
\section{Language rules}

Same as qnx-micro (inherited):
\begin{enumerate}[leftmargin=2em]
\item C++26, modules only, no \texttt{\#include} (except test files for Catch2).
\item LLVM Clang 22+ only.
\item No external C++ libraries beyond the kernel and Catch2.
\item All qnx-micro coding rules apply: \texttt{[[nodiscard]]},
  designated initializers, no throw/catch, no raw pointers,
  no mutable/volatile (except \texttt{hal.cppm} for MMIO),
  value semantics, Rule of Zero.
\item SPDX license header on every source file.
\end{enumerate}

%%% ===================================================================
\section{Architecture}

\begin{Verbatim}[fontsize=\small,frame=single]
~/qnx-micro/build/     (read-only kernel: PCMs + .o files)
     |
     | import qnx.kernel
     v
~/rp4/src/hal/hal.cppm  (BCM2711 hardware abstraction)
     |
     | import rp4.hal
     v
~/rp4/src/apps/*.cpp    (resource managers: audiomgr, etc.)
     |
     | bare-metal
     v
~/rp4/src/boot/         (startup, vectors, linker script)
\end{Verbatim}

%%% ===================================================================
\section{Verification pyramid}

\begin{enumerate}[leftmargin=2em]
\item \textbf{C++26 types} --- compile-time, every build.
\item \textbf{Catch2 tests} --- host build, exercises app logic
  against the kernel model.
\item \textbf{Z3 via alloy-fsx} --- \texttt{spec/verify\_audio.fsx},
  proves capability invariants for the audio manager.
\item \textbf{Doxygen ratchet} --- coverage monotonically increases.
\end{enumerate}

%%% ===================================================================
\section{Pre-commit hook}

Three gates:
\begin{enumerate}[leftmargin=2em]
\item \textbf{Quick checks} --- bans \texttt{\#include}, raw ptrs,
  external libs, mutable/volatile (exempt: hal.cppm).
\item \textbf{Build gate} --- project must compile.
\item \textbf{Z3 gate} --- if \texttt{spec/*.fsx} changed,
  all assertions must prove UNSAT.
\item \textbf{Doxygen ratchet} --- if \texttt{src/*.cppm} changed,
  no doc coverage regression.
\end{enumerate}

%%% ===================================================================
\section{What not to do}

\begin{enumerate}[leftmargin=2em]
\item Never modify \texttt{\textasciitilde/qnx-micro}.
\item No \texttt{.md} files.  LaTeX only.
\item No undocumented public API.
\item No new app without Catch2 tests.
\item No capability grant without Z3 assertion proving no escalation.
\item No MMIO access outside \texttt{hal.cppm}.
\item No ASCII art in \texttt{.tex} files.  TikZ only.
\end{enumerate}

\end{document}
